---
title       : Developing Data Products Course Poject
subtitle    : Shiny Application - Body Mass Index Calculator 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax,quiz,bootstrap]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Body Mass Index Calulator

This application calculates the Body Mass Index (BMI) of a user based on the user's weight and height. The user enters his/her weight in pounds and height in inches.

The application displays:
  + The weight entered in pounds
  + The height entered in inches
  + The calculated BMI
  + The categorization of the BMI as "underweight", "normal", "overweight", or "obese" 

---
## Formula
The formula used for calculating the BMI in the US system is:


$$BMI = \frac{{weight~in~pounds} \times 703}{(height~in~inches)^2}$$


-------------------------
## Weight Category based on BMI


```{r,echo=FALSE}

BMI <- c("Below 18.5", "18.5 - 24.9", "24.9 - 29.9","Above 29.9")
Category <- c("underweight","normal","overweight","obese")
df <- data.frame(BMI,Category)

```
```{r createtable, results='asis', echo=FALSE}

cat("BMI | Weight Category", "--- | ---", sep="\n")
cat(apply(df, 1, function(X) paste(X, collapse=" | ")), sep = "\n")

```

-------
## References

The formula for the BMI used in this application is take from the website:


<http://www.whathealth.com/bmi/formula.html>

--------
